\subsection{Configuring device into local Loggernet (or PC200W)}
\paragraph{}
Connection in local environment is accomplished by a serial RS232 serial connection. While PC200W is distributed as free software, Loggernet is offered both in a paid version and a 30-day trial version. PC200W can be downloaded from \cite{cs1}. Loggernet trial version can be downloaded from \cite{cs2}
\paragraph{Serial link requirements}
To connect device via serial link user has to install a driver for the serial-to-USB adaptor, that can be downloaded from \cite{prol1}. 
\paragraph{Adding device}
Once the device is connected, user can now open Loggernet and click on {\tt Set-up} in {\tt Main} tab. If it's the first time running Loggernet (or PC200W), it will open the {\tt EZSetup Wizard}, 
otherwise user has to click on {\tt Add} button located in the tool-bar (if using Loggernet, make sure Set-up is running in simplified mode by checking it in the title bar. If not, click on the button {\tt EZ View} on the toolbar).
\begin{enumerate}
	\item In {\tt Communication Set-up} section choose CR1000 and go to the next step.
	\item Then choose connection type {\tt Direct}
	\item Select COM port to connect with (check Windows' Device Manager to discover COM port, it should display {\tt Prolific USB to Serial adaptor}).
	\item Set {\tt Baud rate} at {\tt 9600} and {\tt PakBus Address} at {\tt 1}.
	\item Skip the following {\tt Datalogger settings} by pressing Next if not using any type of encryption.
	\item Check chosen parameters in {\tt Set-up summary}
	\item Verify parameters in {\tt Communication Test} by clicking {\tt Next}
	\item If test passes, in the following tab set the datalogger clock by clicking {\tt Check Datalogger Clock}
	\item Select and send a program to the datalogger by clicking on {\tt Select and Send program}
	\item \emph{Only for Loggernet:} click on {\tt Get table definition} to retrieve table structures from the datalogger as defined in the program
	\item \emph{Only for Loggernet:} enable {\tt Scheduled collection }  and set the time  and interval for automatic data collection.
	\item Click {\tt Finish} to close the wizard.
\end{enumerate}
\paragraph{}
Added device can now be seen by pressing {\tt Set-up} in {\tt Main} tab.